//Alex Steel
//Graduation Dox
//March 18
=BEGIN
Over 10 years ago, I started out with no knowledge of what the hell a damn program was.
All I knew was that I was much like the thing I was fucking starting at.
I had an xbox 360 at the time, and the main video games were Halo and Call of duty.
We played, and Video Games made me want to learn how to do all this shit.
I am sitting here in a virtual world, entirely different than the real world, probably better.
Well, guess I might as well learn how to write a code.
I opened up my xbox 360 did some quick fix soldering and hooked that bitch up to my computer.
Time to dump that shit. For fucks sake if i ever brick it, i better be able to rebuild it.
nandpro nand.bin: -r16 kv.bin 1 1
nandpro nand.bin: -r16 config.bin 3de 2
nandpro xbr.bin: -w16 kv.bin 1 1
nandpro xbr.bin: -w16 config.bin 3de 2
nandpro lpt: -w16 xbr.bin
Waiting for DHCP ......... FAIL!
starting httpd server .. OK!
fuseset 00: c0ffffffffffffff
fuseset 01: 0f0f0f0f0f0f0f0f
fuseset 02: 0f00000000000000
fuseset 03: ba450c998dc09a6b
fuseset 04: 7772ee9554c6c8e3
fuseset 05: ff00000000000000
Basically after a bunch of fun stuff. I haz homebrewz on sexBawx.
Now. Call of duty. Not necessarily interesting as MP game servers 
did not have active ban support. Occasionally if you fucked up enough, 
you would just overload the score buffer and it would reset into the negatives.
219746512738916 Was around the maximum score one could obtain in the game.
So if you capped over it, it would just reset you into the negatives, and a score
could become -219746512738916 and you would go from first to last in a ms.
More importantly. Halo was fun, because back in the olden days, Bungie had
and incredibly proactive ban hammer. The most obtainable piece of armor
was known as the Flaming Recon Helmet. Recon Helmets could only be obtained
from beating the game on the hardest difficulty, Obtain all hidden Skulls and collectables
as well as getting a certain score in a survival type game mode. Originally, there was only
one way to get a Recon Helmet. Impress the Devs so much that they basically suck your dick
and give you one, and that rarely happened. Only in community events with user levels in the millions.
So the udds of getting a Recon Helmet were slim, but with the new collectable system, I got it.
Now that isn't the interesting thing. Recon was available to the public after a certain time,
due to the Devs wanting to thank such a hardworking community. Flaming Recon Helmets were
reserved specifically for Devs. 
So... I got it.
Within each game, there is a certain attribute that determines the Armor Sets.
After the public addition to Recon Helmets, it was not much effort to spoof Devs.
Now, due to the proactive ban hammer deployed by the Devs. Hax || Modifications to this degree
would probably be sniffed out in around 7-10 hours. A short program giving _id to all devs
would mean that my _id was not in that program. Therefore I would get a ban, if they caught me.
Because Microsoft had a more advanced illegal hardware detector. The entire console would receive
a _id ban @ ~5 hours, depending on levels of modifications. 
So my console gets banned. GREAT. Dump the key vault storing console_id and information
then get a nubs. Thankfully, I had a few extra key vaults from all my Red Ringed xbox's.
Red Ring means BSOD. xDxDxDxDxD. Might be bricked, but it aint banned. So i gotz a bypass.
Anyway, long story short. I consider myself a hacker. Not by the fact that I want to collect data,
but because of the way I think, and my desire to learn as much as I can. 
Within my time at Butler University. I was severely unhappy. While I wanted to study computer science,
there was not a single person at this school that could point me where I wanted to study.
I wasted everything. Time, Money and Respect. I just wanted to do something that made me happy,
and that was a direct ticket to wasteland. Where all are welcome, and I have called my home. 
I tried, and tried. But I know nothing. What was this even for? I forgot along the way. 
I cared so much about passing, because that is all that mattered. Making my parents proud because
I got a piece of paper. I failed you. I failed myself. And most regrettably, I failed my parents.
These past 5 years were spent learning all the ways to wasteland, instead of making my own.
I probably won't be successful. I probably will spend my life working dead end jobs, never
living up to my potential because I failed the most important game. How to learn.
I use others and their resources without making my own. And it sucks. My entire life
is dependent on that piece of paper. With it, or without it, I feel I am not destined for this.
There were times when I was truly happy. I felt as if I was learning, and that effort payed off.
I never realized how hard I made it for everyone, when everyone just wanted me to win.
G, J, C, B, P, and NP. They all pushed me. And each and every one of them must have been crushed when they
found out that it was all wasted. I thought that this was just hurting me. But no. I hurt each of you.
I put all of it on my shoulders. And it kept crumbling. I built myself on a broken foundation.
WubbaLubbaDubDub. I am in great pain. Please help me. Let me out, what you see is not the 
same person as me. My life's a lie, im not who you're looking at. Let me out, set me free
I am really old, this isnt me, my real body's slowly dying in a vat. Is anybody listening,
and can anyone understand. Stop looking at me like that and actually help me.
Help Me, help me, im gonna die. What is my purpose. I pass butter. Yeah, welcome to the club pal.
[YOU] make {ME} write {MY} version of [YOUR] game.
[WE] should [FIND] more [RESOURCES] so [WE] csprog [CAN] thrive [IN] no [TIME]
Upon graduation, I will be pursuing my true desires. The pursuit of cyber security.
I will be writing my own operating system and server to play games such as CTF
in an attempt to become a PenTester. 
=END

Yes, I am a criminal. My crime is that of curiosity. 
My crime is that of judging people by what they say and think. 
Not what they look like.

FinalReport.Continued = 'FinalReport.tex'
Crypt: TCCJWTPIIOBPPCEAPLJIZEXGR 
Key: TRYME
Plain: ALEXSTEELWILLRISEASAHAXOR
